---
title: "Marketing Analytics HW1"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Innovation: Cruz BlenderCap
Look alike: Blenders

The Cruz BlenderCap stands out as an innovative and portable blending solution, allowing users to turn their regular wide-mouth water bottles into powerful blenders. In contrast, traditional blenders, while effective, are typically bulkier and confined to kitchen spaces. The Cruz BlenderCap takes portability and convenience to a new level, making it ideal for people who want to blend smoothies, shakes, or other beverages on the go. Its cordless design and compatibility with various water bottles make it distinct from traditional, stationary blenders.

In terms of technology, traditional blenders have evolved to offer high-powered blending, but they are limited by their size, weight, and the need for dedicated containers. The Cruz BlenderCap, however, leverages modern battery technology and compact design to offer similar blending power in a more versatile, portable form. This innovation opens new market possibilities, particularly for health-conscious, active consumers who value convenience and mobility, whereas traditional blenders are more suited for home use. The Cruz BlenderCap offers a solution for modern, on-the-go lifestyles, thus expanding the market beyond the kitchen.

```{r}
#install.packages("readxl")
#install.packages("cli")
#install.packages("ggplot")
#install.packages("gridExtra")
# Load ggplot2 for plotting
#install.packages("tidyverse")
#library(tidyverse)
#library(ggplot2)
library(gridExtra)
install.packages("farver")
```

```{r}
# Load necessary libraries
library(readxl)

# Read the data from the Excel file
blender_sales_data <- read_excel("/Users/apple/Downloads/blender_sales.xlsx")

# Extract sales and time variables
sales <- blender_sales_data$`Annual sales`
t <- 1:length(sales)

# Fit the Bass diffusion model
bass_m <- nls(sales ~ m * (((p + q)^2 / p) * exp(-(p + q) * t)) / ((1 + (q / p) * exp(-(p + q) * t))^2),
              start = list(m = sum(sales), p = 0.02, q = 0.4))

# Output the summary of the model
summary(bass_m)
```

```{r}
p <- coef(bass_m)["p"]
q <- coef(bass_m)["q"]

cat("Coefficient of innovation (p):", format(round(p, 5), nsmall = 5), "\n")
cat("Coefficient of imitation (q):", format(round(q, 5), nsmall = 5), "\n")
```

According to Cognitive Market Research, the global Household Blender market size is USD 2158.2 million in 2024 (source: https://www.cognitivemarketresearch.com/household-blender-market-report) and the average price of blenders is around 100$, this means approximately 21.58 million units are sold globally. Cruz BlenderCap is bit pricier than the average blender, therefore let's assume only around 60% of people will be able to afford it or would consider buying it for that price. Therefore, it equals to 12,948,000 units.
Then let's assume only 20% of that will actually buy the product, therefore we get 2,589,600, which we can consider as our potential market for the chosen product.

```{r}
# Define the Bass model function
bass_model <- function(t, p, q, M) {
  exp_term <- exp(-(p + q) * t)
  return(M * (((p + q)^2 / p) * exp_term) / (1 + (q / p) * exp_term)^2)
}

# Bass model parameters (global scope)
M <- 2589600  # Market potential (units, globally)
p <- 0.03315    # Coefficient of innovation
q <- 0.16044   # Coefficient of imitation
years <- 1:10  # Time period of 10 years

# Calculate the number of adopters for each year
adopters <- bass_model(years, p, q, M)

# Create a data frame for the years and adopters
df <- data.frame(Year = years, Adopters = round(adopters))

# Plot the diffusion curve
plot(df$Year, df$Adopters, type = "o", col = "blue", xlab = "Years", ylab = "Number of Adopters", 
     main = "Predicted Diffusion of Cruz BlenderCap (Bass Model)")
grid()

# Print the estimated number of adopters for each year
print(df)

# Optionally, you can calculate the cumulative number of adopters by summing year by year
df$Cumulative_Adopters <- cumsum(df$Adopters)

# Print the cumulative data
print(df)

```

```{r}
# Define the Bass model functions
bass.f <- function(t, p, q) {
  return(((p + q)^2 / p) * exp(-(p + q) * t) / (1 + (q / p) * exp(-(p + q) * t))^2)
}

bass.F <- function(t, p, q) {
  return((1 - exp(-(p + q) * t)) / (1 + (q / p) * exp(-(p + q) * t)))
}

# Bass Model parameters (use the optimized parameters from your model)
m <- 2589600  # Market potential
p <- 0.03315     # Coefficient of innovation
q <- 0.16044     # Coefficient of imitation
t <- 1:10    # Time periods (10 years)

# Predict the number of adopters per period
pred <- bass.f(t = t, p = p, q = q) * m
pred_df <- data.frame(Year = t, Adopters = pred)

# Predict cumulative adopters
pred_cumulative <- bass.F(t = t, p = p, q = q) * m
pred_cumulative_df <- data.frame(Year = t, Cumulative_Adopters = pred_cumulative)



# Plot number of new adopters per year
p1 <- ggplot(pred_df, aes(x = Year, y = Adopters)) +
  geom_line(color = "blue") +
  ggtitle("Number of Adoptions per Year") +
  xlab("Years") + ylab("Number of Adopters")

# Plot cumulative adopters over time
p2 <- ggplot(pred_cumulative_df, aes(x = Year, y = Cumulative_Adopters)) +
  geom_line(color = "green") +
  ggtitle("Cumulative Adoptions Over Time") +
  xlab("Years") + ylab("Cumulative Adopters")

# Arrange the two plots side by side
grid.arrange(p1, p2, ncol = 2)

# Print data frames for adopters and cumulative adopters
print(pred_df)
print(pred_cumulative_df)

```

